\documentclass{ximera}

%\input{preamble.tex} %% we can turn off input when making a master document

\outcome{Conditional and independent probability.}

\title{Conditional probability.}

\begin{document}
\begin{abstract}
Conditional and independent probability.
\end{abstract}
\maketitle

\begin{question}
Suppose:

$P(\text{rain today})=40\,\%\,$; 

$P(\text{rain tomorrow})=50\,\%\,$; 

$P(\text{rain today and tomorrow})=30\,\%\,$.

Given that it rains today, what it is the chance that it will rain tomorrow ?
     \begin{solution}
           The answer is \answer{$75$} $\%$.
     \end{solution}
\end{question}

\begin{question}
There are two urns. The first urn contains $2$ black balls and $3$ white balls. The second urn contains $4$ black balls and $3$ white balls. An urn is chosen random, and a ball is chosen at random from that urn.

a) Draw a suitable tree diagram.

b) Assign probabilities and conditional probabilities to the branches of the tree.

c) Calculate the probability that the ball drawn is black.
     \begin{solution}
           The answer is \answer{$17/35$}.
     \end{solution}
\end{question}

\begin{question}
A hat contains a number of cards, with

$30\,\%$ white on both sides;

$50\,\%$ black on one side and white on the other;

$20\,\%$ black on both sides.

The cards are mixed up, then a single card is drawn at random and placed on the table. If the top side is black, what is the chance that the other side is white ?
     \begin{solution}
           The answer is \answer{$5/9$}.
     \end{solution}
\end{question}

\end{document}