\documentclass{ximera}

%\input{preamble.tex} %% we can turn off input when making a master document

\outcome{learn about Normal and Poisson approximations.}

\title{Approximations.}

\begin{document}
\begin{abstract}
Normal and Poisson approximations.
\end{abstract}
\maketitle

Let $X_{1}, X_{2}, \dots, X_{100}$ be independent uniform (continuous) distributions on the interval $(0,4)$. Let $S$ denote the sum $\sum_{j=1}^{100} X_{j}$. Use normal approximation to approximate

\begin{question} 
     \begin{solution}
          $P(195\leq S \leq 210) = $  \answer{$0.47$}. (Round to two decimals)
     \end{solution}
\end{question}

A fair coin is tossed $10,000$ times. Find a number $m$ such that the chance of the number of heads being between $5000-m$ and $5000+m$ is approximately $2/3$.

\begin{question}
    \begin{hint}
         $m$ must be an integer.
    \end{hint}
     \begin{solution}
          The number $m$ is \answer{$48$}
     \end{solution}
\end{question}

Wonderful Widgeds Inc. has developed electronics devices which work properly with probability $0.95$, independently of each other. The new devices are shipped out in boxes containing $400$ each.

\begin{question}
     a) What percentage of boxes contains $390$ or more working devices ?
     \begin{solution}
           The percentage is \answer{$0.01$} (Round to two decimals).
     \end{solution}
\end{question}

\begin{question}
     b) The company wants to guarantee, say, that $k$ or more devices per box work. What is the largest $k$ such that at least $95\,\%$ of the boxes meet the warranty ?
     \begin{solution}
           The number $k$ is \answer{$373$}.
     \end{solution}
\end{question}

Let $X$ have a Binomial $(500,0.02)$ distribution. Use Poisson approximation to determine the probability of the following

\begin{question} 
     \begin{solution}
          $P(X=12) = $  \answer{$(39062500e^(-10))/(18711)$}.
     \end{solution}
\end{question}

\begin{question} 
     \begin{solution}
          $P(X<3) = $  \answer{$61e^(-10)$}.
     \end{solution}
\end{question}

Let $Y$ have Poisson distribution with mean $4.1$. 

\begin{question}
     \begin{hint}
          Compute $\frac{P(Y=k+1)}{P(Y=k)}$.
     \end{hint} 
     \begin{solution}
          The mode of $Y$ is  \answer{$4$}.
     \end{solution}
\end{question}

\end{document}
