\documentclass{ximera}

%\input{preamble.tex} %% we can turn off input when making a master document

\outcome{to learn definition and properties of random variables.}

\title{Random variables.}

\begin{document}
\begin{abstract}
basic definitions
\end{abstract}
\maketitle

A {\it random variable} $X$ is a function with domain the sample space and range a subset of the real numbers. Because the value of a random variable is determined by the outcomes of the experiment, we may assign probabilities to the possible values of the random variable. \vspace{.35cm} 

\begin{question}
Three dice are rolled. What is the probability that the total number of spots showing is $11$ or more ?
     \begin{hint}
          No long calculations ! 
     \end{hint}
     \begin{solution}
          The probability is equal to \answer{1/2}.
     \end{solution}
\end{question}

\begin{question}
Find a number $m$ such that if five dice are rolled, the probability that the total number of spots showing is $m$ or more is the same as the probability of $11$ or more spots from three dice.
     \begin{hint}
          $m$ is an integer.
     \end{hint}
     \begin{solution}
          The number $m$ is equal to \answer{18}.
     \end{solution}
\end{question}

Let $X$ be the number of heads in $15$ fair coin tosses, $Y$ a number picked uniformly at random from $\{\, 0,1,\dots,15 \,\}$, independently of $X$. Let $Z = max(X,Y)$.

\begin{question}
     \begin{solution}
           Determine $P(Z=5) = $ \answer{19959/524288}.
     \end{solution}
\end{question}

(Think about the following setup, it can help you to calculate the previous probability) For the previous problem, find a formula for $P(Z=k)$ which will depend on $k$, for $k=0,1,\dots,15$. \vspace{.35cm}

Let $X_{1}$ and $X_{2}$ denote the number obtained on two rolls of a fair die. Let $X=min(X_1, X_2)$ and $Y=max(X_1, X_2)$.

\begin{question}
     \begin{solution}
          Determine $P(X=Y) = $ \answer{1/6}.
     \end{solution}
\end{question}

\begin{question}
     \begin{solution}
          Determine $P(X<Y) =$ \answer{5/6}.
     \end{solution}
\end{question}

Suppose a fair die rolled eight times. Find numerical values for the expectations of each of the following random variables.

\begin{question}
     a) The sum of the numbers in the eight rolls
     \begin{solution}
          The required expectation is \answer{28}.
     \end{solution}
\end{question}

\begin{question}
     b) The maximum number in the first three rolls.
     \begin{solution}
          The required expectation is \answer{119/24}.
     \end{solution}
\end{question}

\begin{question}
     c) The number of multiples of three in the eight rolls.
     \begin{solution}
          The required expectation is \answer{8/3}.
     \end{solution}
\end{question}

\begin{question}
     d) The number of faces which fail to appear in the eight rolls.
     \begin{solution}
          The required expectation is \answer{390625/279936}.
     \end{solution}
\end{question}

\begin{question}
     e) The number of different faces that appear in the eight rolls.
     \begin{solution}
          The required expectation is \answer{1288991/279936}.
     \end{solution}
\end{question}

\end{document}